\Large \bf CS380S: Project Proposal

### 2018-09-17 proposal/proposal.tex
Updates
updated

We plan to use Data Dependency tools to determine how system entropy in a given program is used by various cryptographic algorithms. That will allow us to identify if and when entropy is too low or is misused. We can release this as a tool for developers to use as part of a compiler toolchain. We can also use the tool on current projects that might be misusing crypto/entropy.

We have two motivating examples. First, we would like our tool to be able to detect the issue with the Debian/OpenSSL pseudo-random number generator that was exposed in 2008. Second, we would like to identify potential vulnerabilities in current cryptocurrency wallet code.

@@

\begin{enumerate}
	\item Determine data dependency tool (for C/C++) to use, conduct background research (\textit{2 weeks})
	\item Adapt tool to identify the OpenSSL bug (\textit{6 weeks})
	\item Test on other cases like bitcoin wallets (\textit{2 weeks})
	\item Prepare presentation/writeup (\textit{1 week})
	\item Integrate tool into compiler toolchain like clang (\textit{optional})
\end{enumerate}

\section{Research Hypothesis}

@@

% TODO maybe we need to say what exactly we found in the links instead of just dropping links?
\subsection{Background information}

\begin{enumerate}
	\item Debian/OpenSSL Bug 
		\begin{enumerate}
			\item \url{https://www.schneier.com/blog/archives/2008/05/random_number_b.html}
			\item \url{https://research.swtch.com/openssl}
			\item \url{https://freedom-to-tinker.com/2013/09/20/software-transparency-debian-openssl-bug/}
			\item \url{https://www.cs.umd.edu/class/fall2017/cmsc818O/papers/private-keys-public.pdf}
		\end{enumerate}
	\item Data flow
		\begin{enumerate}
			\item \url{https://en.wikipedia.org/wiki/Data-flow_analysis}
			\item \url{https://www.seas.harvard.edu/courses/cs252/2011sp/slides/Lec02-Dataflow.pdf}
		\end{enumerate}

@@

\subsection{Related research}

>>>>

\subsection{Motivation}
One common misuse of cryptography is the misuse of entropy. Without proper random inputs, many cryptographic algorithms
are vulnerable to basic forms of cryptanalysis. Some cryptographic schemes, such as DSA, can even disclose long-term secrets
like the signing key when the random per-message input is low entropy, made public, or nonunique.

We have two motivating examples. First, we would like our tool to be able to detect the issue with the Debian/OpenSSL pseudo-random number generator that was exposed in 2008. 
Second, we would like to identify potential vulnerabilities in current cryptocurrency wallet code as many cryptocurrency protocols rely on DSA.

\subsection{Goals}
We plan to use data dependency tools to determine how entropic inputs in a given program are used by various cryptographic algorithms. 
That will allow us to identify if and when entropy is too low or is misused. We plan to either produce
this as a code integration tool for developers to use as part of a compiler toolchain, or use this tool to analyze a large number of codebases
found ``in the wild,'' such as those written by amateurs.

Our tool will seek to generate a human-checkable dependency graph from source code
using taint analysis on functions and function inputs manually specified via annotation by the developer.
This graph will allow the developer to manually verify that entropy is used properly; a stretch goal 
of ours would be to automate the identification of a subset of known misuses of entropy.

@@

\begin{enumerate}
	\item Determine data dependency tool (for C/C++) to use, conduct background research (\textit{2 weeks})
	\item Adapt tool to identify the OpenSSL bug (\textit{5 weeks})
	\item Test on other cases like Bitcoin wallets (\textit{3 weeks})
	\item Prepare presentation/writeup (\textit{1 week})
	\item Integrate tool into compiler toolchain like clang (\textit{optional})
\end{enumerate}

\section{Research Hypotheses}

We principally have two hypotheses we would like to test.

@@

Static code analysis has a history of identifying security vulnerabilities at a source code level.
Some examples include SQL injection, cross-site scripting exploits, and buffer overflow attacks. However,
there has not been any attempt in the literature to statically analyze source code for cryptographic
vulnerabilities stemming from entropy misuse, which we seek to do.

% TODO maybe we need to say what exactly we found in the links instead of just dropping links?

\begin{enumerate}
	\item Debian/OpenSSL Bug 
		\begin{enumerate}
			\item \url{https://www.schneier.com/blog/archives/2008/05/random_number_b.html}
			\item \url{https://research.swtch.com/openssl}
			\item \url{https://freedom-to-tinker.com/2013/09/20/software-transparency-debian-openssl-bug/}
			\item \url{https://www.cs.umd.edu/class/fall2017/cmsc818O/papers/private-keys-public.pdf}
		\end{enumerate}
	\item Data flow
		\begin{enumerate}
			\item \url{https://en.wikipedia.org/wiki/Data-flow_analysis}
			\item \url{https://www.seas.harvard.edu/courses/cs252/2011sp/slides/Lec02-Dataflow.pdf}
		\end{enumerate}
	\item Static Program Analysis
		\begin{enumerate}
            \item \url{https://cs.au.dk/~amoeller/spa/spa.pdf}
            \item \url{https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=6859783}
		\end{enumerate}

@@
